### 2016-03-02 Docs/managing_jobs/managingjobs.tex
no longer need special tweaks for intel
more NERSC notes

{\em Not sure if this still applies: Note that with the Intel compilers, you should never use the {\tt -ss}
option to {\tt aprun}, and should use {\tt -cc depth} for $< 12$
threads and {\tt -cc numa\_node} for $12$ threads.}

@@

The same set of submission scripts described for titan are available
for edison at NERSC in {\tt Util/job\_scripts/edison/}.  They are
mostly identical, with a few minor changes for the local system
configuration.  The use is the same as described above.

>>>>

To chain jobs, such that one queues up after the previous job finished,
use the {\tt chainslurm.sh} script in that same directory.

@@

The same set of submission scripts described for titan are available
for edison at NERSC in {\tt Util/job\_scripts/edison/}.  In particular,
the job submission script will set the restart command line parameters
to restart from the most recent checkpoint file in the output directory.

Note: NERSC does not allow for the {\tt process} script that archives
to HPSS to run in the main job submission script.  Instead, a separate
job needs to be run in the ``{\tt xfer}'' queue.  The script {\tt edison.xfer.slurm} 
in {\tt Util/job\_scripts/edison/} shows how this works.

Jobs in the {\tt xfer} queue start up quickly.  The best approach is
to start one as you start your main job (or make it dependent on the
main job).  The sample {\tt process.xrb} script will wait for output
and then archive it as it is produced, using the techniques described
for titan above.

To check the status of a job in the {\tt xfer} queue, use:
\begin{verbatim}
squeue -u username -M all
\end{verbatim}
